Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection

### 2022-07-11 article.Rnw
minor

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Comparing binsegRcpp with other implementations of binary segmentation}
\Plaintitle{A Short Demo Article: Regression Models for Count Data in R}
\Shorttitle{A Short Demo Article in \proglang{R}}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Achim Zeileis\\
  Journal of Statistical Software\\
  \emph{and}\\
  Department of Statistics\\
  Faculty of Economics and Statistics\\
  Universit\"at Innsbruck\\
  Universit\"atsstr.~15\\
  6020 Innsbruck, Austria\\
  E-mail: \email{Achim.Zeileis@R-project.org}\\
  URL: \url{https://www.zeileis.org/}
}

>>>>

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection}
\Plaintitle{Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection}
\Shorttitle{binsegRcpp for changepoint detection}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Toby Dylan Hocking\\
  School of Informatics, Computing and Cyber Systems\\
  Northern Arizona University\\
  1295 S. Knoles Dr.\\
  Flagstaff, AZ 86011\\
  E-mail: \email{Toby.Hocking@R-project.org}\\
  URL: \url{https://www.zeileis.org/}
}
